---
title: "SampleSuperstore Analysis"
author: "Ridam Pal Singh"
date: "06/12/2020"
output: pdf_document
---
Importing the required libraries
```{r}
library(dplyr)
library(ggplot2)
library(corrplot)
library(flexdashboard)
library(rmarkdown)
```

##Reading the datafile

```{r}
superstore <- read.csv("/Users/ridamsingh/Desktop/SampleSuperstore.csv")
```

##Some elements of the dataset

```{r}
glimpse(superstore)
head(superstore)
```

##Summary of the data

```{r}
summary(superstore)
```
##Observations

From this we can makeout that there are total of 13 variable in the dataset.


##Removing rows with duplicate data

```{r}
superstore <- distinct(superstore)
```

##Data Visualisation

1) Histogram and Boxplots for numerical data

```{r}
ggplot(superstore,aes(x=Sales,fill=Sales)) + geom_histogram(binwidth = 600) + ggtitle("Sales") + xlim(0,5000) + ylim(0,2000)
ggplot(superstore,aes(x=Sales)) + geom_boxplot()

```

```{r}
ggplot(superstore,aes(x=Discount)) + geom_histogram(aes(fill='clarity')) + ggtitle("Discount")
ggplot(superstore,aes(x=Discount)) + geom_boxplot()
```


```{r}
ggplot(superstore,aes(x=Profit)) + geom_histogram(aes(fill='clarity')) + ggtitle("Profit")  + xlim(-1500,2000)
ggplot(superstore,aes(x=Profit)) + geom_boxplot()
```

##Comparing the Sales and Profits


```{r}
ggplot(superstore,aes(Sales)) + geom_density(aes(fill='RED')) + xlim(0,1000) + geom_density(aes(x=Profit))
```
##Correlation plots between Sales , Qunatity , Discount and Profit

```{r}
a <- select(superstore,10:13)
corrplot(cor(a),method = 'number')
corrgram::corrgram(a)
```
# Observations
1) We can see a positive correlation between Sales and Profit 
2) A negative correaltion between Discount and Profit.
3) The Quantity and Profit do not look related.
-------------------------------------------------------------------------------------------------------------------------------------------------------------------


##Correlation plots between each category.
```{r}
pairs(a)
```

Total Sales Analysis 

According to States

```{r}
statewise_sales <- superstore %>%
                  group_by(State) %>% 
                  summarise(Total_Sales= sum(Sales)) %>%
                  arrange(desc(Total_Sales))
statewise_sales
```

Plotting the total sales statewise

```{r}
ggplot(superstore,aes(x=State,y=Sales,fill=State)) + geom_col() + ggtitle("Total Sales in each State") + coord_flip() + theme(legend.position = 'None' , axis.text.y = element_text(size  = 5))
```


According to Regions


```{r}
region_sales <- superstore %>%
                  group_by(Region) %>% 
                  summarise(Total_Region= sum(Sales)) %>%
                  arrange(desc(Total_Region))
region_sales

```
Plotting the sales region wise
```{r}


ggplot(superstore,aes(x=Region,y=Sales,fill=Region)) + geom_col() + ggtitle("Total Sales in each Region") + coord_flip()

```

#Observations
1) The highest total number of Sales of the SuperStore is done in California followed by New York.
2)Then the sales are dratically decreasing in other states.
3)The least sales is seen by States of North Dakota and Virginia.
4) Most number of sales is done by the West and East Regions of the country.
-------------------------------------------------------------------------------------------------------------------------------------------------------------------


##Profit Analysis

Total Profit according to States

```{r}
statewise_profit <- superstore %>%
                  group_by(State) %>% 
                  summarise(Total_Profit= sum(Profit)) %>%
                  arrange(desc(Total_Profit))
statewise_profit
```


```{r}
ggplot(superstore,aes(x=State,y=Profit,fill=State)) + geom_col() + ggtitle("Total Profit in each State") + coord_flip() + theme(legend.position = 'None' , axis.text.y = element_text(size  = 5))
```
Region wise analysis of total profit

```{r}

region_profit <- superstore %>%
                  group_by(Region) %>% 
                  summarise(Total_RegionP= sum(Profit)) %>%
                  arrange(desc(Total_RegionP))
region_profit


```

```{r}
ggplot(superstore,aes(x=Region,y=Profit,fill=Region)) + geom_col() + ggtitle("Total Profit in each Region") + coord_flip()
```


#Observations 
1) The major profit making States were California and NewYork which also had the most number of Total Sales.
2) Major loss making states were Texas and Ohio.
3) The most profitable region for the store is East and West also having the most number of Sales.
-------------------------------------------------------------------------------------------------------------------------------------------------------------------

##Citywise Analysis of Sales and Profits

```{r}
m <- group_by(superstore,City)

n <- m %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales),
                Qunatity=sum(Quantity))
n <- arrange(n,desc(Sales))
n
```
#Observations

1) New York is with maximum Sales , Profit and Quantity.
2) Philadalphia is the the most loss making city.
3) Abilene is the city with the least sales.

-------------------------------------------------------------------------------------------------------------------------------------------------------------------


## Analysis of Catogories sold by the store 

```{r}
table(superstore$Category)
```
#Observation
We can see their are total 3 types of categories sold by the superstore out of which Office supplies is the most sold category.

Now lets get into which category gives more sales,profit and quantity using the mean of these values.
-------------------------------------------------------------------------------------------------------------------------------------------------------------------

```{r}
c <- group_by(superstore,Category)

d <- c %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales),
                Qunatity=sum(Quantity))
d <- arrange(d,desc(Sales))
d
```


Visualising the above data of categories.


```{r}
par(mfrow=c(1,2))
pie(d$Profit,labels = d$Category , main = 'Profits with Category',col = rainbow(length(d$Profit)))
pie(d$Sales,labels = d$Category, main = 'Sales with Category',col = rainbow(length(d$Sales)))

```
# Observations 
1) Ofiice Supplies Category is sold in maximum quantity.
2) Maximum sales and profit that superstore generates comes from Technology Category.
3) The major revenue driver for the store is the Tecnology Category.
4) Furniture is the least profitable category in figures.

-------------------------------------------------------------------------------------------------------------------------------------------------------------------


##Analysis of SubCategory

```{r}
table(superstore$Sub.Category)
```



```{r}
ggplot(superstore,aes(x=Sub.Category,fill=Sub.Category)) + geom_bar() + coord_flip()
```


```{r}
e <- group_by(superstore,Sub.Category)

f <- e %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales),
                Qunatity=sum(Quantity))
f <- arrange(f,desc(Sales))
f
```


```{r}
pie(f$Sales,labels = f$Sub.Category ,radius = 1, main = 'Sales with Sub Category', col = rainbow(length(f$Sales)))
```
# Observations

1)The sub category of Binders , Paper , etc. are the most sold which belong to the category of Office Supplies.
2)Copiers is the least sold sub category.
3)Though least sold in quantity comparitively, copiers and Machines sub category drive the major sales of the superstore.
4)Chairs and Phones make the maimum sales in the store.

-------------------------------------------------------------------------------------------------------------------------------------------------------------------




##Shipping Modes

```{r}
table(superstore$Ship.Mode)
```

```{r}
ggplot(superstore,aes(x=Ship.Mode)) + geom_bar(aes(fill='red'))
```

```{r}
g <- group_by(superstore,Ship.Mode)

h <- g %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales),
                Qunatity=sum(Quantity))
h <- arrange(h,desc(Sales))
h
```

```{r}
par(mfrow=c(1,2))
pie(h$Profit,labels = h$Ship.Mode , main = 'Profits with Shipping Mode',col = rainbow(length(h$Profit)))
pie(h$Sales,labels = h$Ship.Mode, main = 'Sales with Shipping Mode',col = rainbow(length(h$Sales)))
```
#Observations

1)Most preferred mode of shipping is the standard class.
2)The sales generated according to the shipping modes is maximum in standard class.
3)The profit generated according to the shipping modes is maximum in standard class.
4)Very less people opt for same day delivery.
-------------------------------------------------------------------------------------------------------------------------------------------------------------------


##Segment

```{r}
table(superstore$Segment)

```

```{r}
ggplot(superstore,aes(x=Segment,fill=Segment)) + geom_bar()
```

```{r}
o <- group_by(superstore,Segment)

p <- o %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales),
                Qunatity=sum(Quantity))
p <- arrange(p,desc(Sales))
p
```
```{r}
par(mfrow=c(1,2))
pie(p$Sales,labels = p$Segment , main = 'Sales with Segment',radius=1, col = rainbow(length(p$Sales)))
pie(p$Profit,labels = p$Segment , main = 'Profit with Segment',radius=1, col = rainbow(length(p$Profit)))
```
#  Observations

1) Looking at the count table , it is evident that the consumer segment is the most sold segment.
2) The most profitable segment is the consumer segement which also drives the major sales of the store.

-------------------------------------------------------------------------------------------------------------------------------------------------------------------

##Quantity Purchased by indivisual customers
```{r}
table(superstore$Quantity)
```

```{r}
ggplot(superstore,aes(x=Quantity,fill=Quantity)) + geom_bar()
```

```{r}
q <- group_by(superstore,Quantity)

r <- q %>% summarise(Profit=sum(Profit),
                Sales=sum(Sales))
r <- arrange(r,desc(Sales))
r
```

```{r}
par(mfrow=c(1,2))
pie(r$Sales,labels = r$Quantity , main = 'Sales with Quantity',radius=1, col = rainbow(length(r$Sales)))
pie(r$Profit,labels = r$Quantity , main = 'Profit with Quantity',radius=1, col = rainbow(length(r$Profit)))
```
# Observations

1) The count table shows that the major quantiy sold is 2,3 or 4 items.
2) These quantities sold drive major profit and sales of the store.
3) The highest quantity purchased by any consumer is 14 items.

-------------------------------------------------------------------------------------------------------------------------------------------------------------------



